DeepAutoTrack (DAC): Car Trajectory Prediction for Autonomous Driving

### 2017-11-11 paper/cvpr2018/cvpr2018_draft.tex
pool figure add

Driver reaction time is a crucial factor for a human driver to react to the traffic participants. Driver reaction time includes recognising the light has changed, deciding to continue or brake, and if stopping engaging the brake (remove foot from accelerator and apply brake). Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
Therefore, the ability to predict traffic participants' \emph{future} trajectory will greatly benefits the mediated perception approach's driving policy decision making.p

@@

@@

@@

We utilise two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.

@@

\section{Experiments}
\subsection{Dataset collection}
We collect car trajectory evaluation dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.

@@

>>>>

Driver reaction time is a crucial factor for a human driver to react to the traffic participants. Driver reaction time includes recognising the light has changed, deciding to continue or brake, and if stopping engaging the brake (remove foot from accelerator and apply brake). Accident reconstruction specialists commonly use 1.5 seconds~\cite{mcgehee2000driver}.
Therefore, the ability to predict traffic participants' \emph{future} trajectory will greatly benefits the mediated perception approach's driving policy decision making.

@@

\item We present a novel ``tracking-by-detection" framework in the context of autonomous driving to robustly track a car. The proposed framework greatly enhanced the trackers' robustness by updating tracker's target representation, in the meanwhile solving the problem of instance association between frames.

@@

\item We formalise the car trajectory problem into a 3D occupancy grid problem given depth information.

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Experiments}

\subsection{Dataset collection}

Currently, most public datasets with semantic labelling are single frame, static images. Continuous video streams are required for the purpose of car trajectory prediction.
We collect car trajectory prediction dataset based on the SYNTHIA~\cite{ros2016synthia} dataset.
SYNTHIA dataset is a large corpus of synthetic images originally collected for the purpose of semantic segmentation of urban scenes generated by rendering a virtual city created with the Unity development platform.
There are more than 200,000 HD ($760\times1280$) photo-realistic frames from video streams.
Frames are acquired from multiple view-points (up to eight views per location), and each of the frames also contains an associated depth map.

Scene diversity: European style town, modern city, highway and green areas
Variety of dynamic objects: cars, pedestrians and cyclists

Multiple seasons: dedicated themes for winter, fall, spring and summer

Lighting conditions and weather: dynamic lights and shadows, several day-time modes, rain mode and night mode

Automatic groundtruth: individual instances for semantic segmentation (pixelwise annotations), depth, car ego-motion
 of photo-realistic frames rendered from a virtual city and comes with precise pixel-level semantic annonations for 13 classes, \emph{i.e.}: miscellaneous, sky, building, road, sidewalk, fence, vegetation, pole, car, sign, pedestrian, cyclist, lanemarking.

The focus of this paper is on car trajectory prediction on high ways. In the SYNTHIA

Some sample frames with its sementic labels and depth information is shown in Fig. (TODO: TY help to generate the figures).
\subsection{traffic participants detection}

We compared two state-of-the-art approaches: SSD~\cite{liu2016ssd} and Faster-RCNN~\cite{ren2015faster} for detecting the traffic participants.
We use the pretrained detection network on the PASCAL VOC detection dataset~\cite{everingham2015pascal} which has 20 classes and fine-tune the network on the SYNTHIA. Curretnly

A comprehensive survey of speed/accuracy trade-offs for modern convolutional object detectors is presented in~\cite{huang2017speed} and we refer the keen readers to

@@

Future works include conducting experiment on the real-world images.
